### 2019-03-16 papers.tex
Disable the choose your own adventure game

\renewcommand{\thepage}{\roman{page}}
\setcounter{page}{3}
\input{mftpc/banner}
\input{mftpc/slide-intro}

@@

\addtrack
	{Theory}{\textit{Bottles}}
\addpaper
	{Sublinear colorings of 3-colorable graphs in linear time}
	{Thomas Tseng}
	{Keywords: graph coloring, approximation algorithms, analysis of algorithms}
	{SIGBOVIK_2018_paper_3}
	{0cm}
	{}
\addpaper
	{Cubic partitioning of simultaneous antipodal 4-corner-day time spaces}
	{R.\ Welch and G.\ Ray}
	{Keywords: timecube, conspiracy theories, applied mathematics, applied cubism, tuesdays, meridian time, word animals}
	{SIGBOVIK_2018_paper_2}
	{0cm}
	{}
\ainput{mftpc/trail-intro} % Before Stefan and Ben's paper
\addpaper
	{Construction of Eulerian trails in large graphs}
	{Stefan Muller and Ben Blum}
	{Keywords: walk, Eulerian trail, large graph}
	{SIGBOVIK_2018_paper_29}
	{0cm}
	{}
	\addreview{SIGBOVIK_2018_review_29}{0cm}
\addpaper
	{Chess circuits}
	{Ross Dempsey, Sydney Timmerman, and Karl Osterbauer}
	{Keywords: chess, logic, boolean circuits}
	{SIGBOVIK_2018_paper_22}
	{2.5cm}
	{}
\ainput{mftpc/itg-miss}

\addtrack
	{Cryptocurrencies}{\textit{A Dream}}
\addpaper
	{GradCoin:\ A poor-to-poor electronic cash transfer system}
	{Siddhant Jain}
	{Keywords: blockchain, P2P, digital currency}
	{SIGBOVIK_2018_paper_15}
	{0cm}
	{}
\addpaper
	{CommieCoin:\ Seizing the means of crypto-production}
	{Marx van Raasveldt \textit{et al.}}
	{Keywords: communism, crypto-currency, CommieCoin}
	{SIGBOVIK_2018_paper_11}
	{0cm}
	{}
\ainput{mftpc/coin-intro} % Before Rob's paper
\addpaper
	{That's Numberwangcoin!}
	{Robert J.\ Simmons}
	{Keywords: boredom, lost coins, shouty bits, speculative investment, the number 2 which you may remember from school is deadly to humans}
	{SIGBOVIK_2018_paper_27}
	{1cm}
	{}
\ainput{mftpc/pants-multi}
\ainput{mftpc/itg-wayoff}

\addtrack
	{Stochastic Processes}{\textit{Portrait of Markov}}
\addpaper
	{Ritwik density estimation and analysis using real techniques}
	{Ritwik Gupta, Ritwik Das, and Ritwik Rajendra}
	{Keywords: Ritwik, Council of Ritwiks, population density, statistical analysis, deep learning, state of the art, monte carlo, bayesian methods, real computational methods and statistics}
	{SIGBOVIK_2018_paper_5}
	{0cm}
	{}
	\addreview{SIGBOVIK_2018_review_5}{0cm}
\ainput{mftpc/bathroom-intro} % Before Sarah and Ziv's paper
\addpaper
	{On the intractability of multiclass restroom queues with perfect stall etiquette}
	{Sarah Allen and Ziv Scully}
	{Keywords: Markov chain, recursive renewal-reward, poop}
	{SIGBOVIK_2018_paper_30}
	{0cm}
	{}
\ainput{mftpc/itg-decent}
\ainput{mftpc/coin-wrong}

\addtrack
	{Ayyy Eye}{\textit{Afterimage of a Crimson Eye}}
\addpaper
	{PSYCHO:\ PerSonalitY CHaracterizatiOn of artificial intelligence}
	{Achal Dave and Rohit Girdhar}
	{Keywords: interpretability, psychology, deep learning, artificial intelligence, rorschach}
	{SIGBOVIK_2018_paper_8}
	{0cm}
	{}
\addpaper
	{The NUGGET non-linear piecewise activation}
	{Stephen Merity}
	{Keywords: deep learning, neural networks, nugget, nuggets, chicken nuggets, smart}
	{SIGBOVIK_2018_paper_10}
	{0cm}
	{}
\addpaper
	{Substitute teacher networks:\ Learning with almost no supervision}
	{Samuel Albanie, James Thewlis, and Jo\~ao F.\ Henriques}
	{Keywords: substitute, teacher, networks}
	{SIGBOVIK_2018_paper_28}
	{1cm}
	{}
	\addreview{SIGBOVIK_2018_review_28}{0cm}
\ainput{mftpc/coin-right}
\ainput{mftpc/itg-excellent}

\addtrack
	{Parapsychology}{\textit{Get Out of My Head}}
\addpaper
	{This grad student studied parapsychology---and you won't believe what he found}
	{David Edelstein}
	{Keywords: parapsychology, science, experimental design, experimenter effects, philosophy, telepathy}
	{SIGBOVIK_2018_paper_23}
	{0cm}
	{}
	\addreview{SIGBOVIK_2018_review_23}{0cm}
\ainput{mftpc/itg-fantastic}
\ainput{mftpc/trail-float}

\addtrack
	{Art}{\textit{Open Your Third Eye}}
\addpaper
	{Automating art snobbiness:\ Dead duck or phoenix?}
	{Dion Ysus and Oscar I.\ Hernandez}
	{Keywords: automation, art, elite, 1337 dankster, cicada 3301, de Bruijn sequence}
	{SIGBOVIK_2018_paper_14}
	{0cm}
	{}
	\addreview{SIGBOVIK_2018_review_14}{0cm}
\addpaper
	{Toward a historically faithful performance of the piano works of Anton\'in Qwe\v{r}t\'y}
	{William Gunther and Brian Kell}
	{Keywords: G-flat major, F-sharp minor, A-flat harmonic major $\flat$6 $\flat$5, G-sharp harmonic major $\flat$5}
	{SIGBOVIK_2018_paper_21}
	{0cm}
	{}
	\addreview{SIGBOVIK_2018_review_21}{0cm}
\addpaper
	{WordTeX:\ A WYSIPCTWOTCG typesetting tool}
	{Tom Wildenhain}
	{Keywords: Word, Microsoft Word, LaTeX, WordTeX}
	{SIGBOVIK_2018_paper_12}
	{0cm}
	{}
	\addreview{SIGBOVIK_2018_review_12}{0cm}
\ainput{mftpc/trail-int}
\ainput{mftpc/itg-intro}

@@

\addtrack
	{Systems}{\textit{Wheel}}
\addpaper
	{mallocd:\ designing a garbage-free nosql data store}
	{igor}
	{Keywords: state-of-the-art, in-memory, garbage-free, cloud-native, nosql, bare metal, containerless, micro-service, data store}
	{SIGBOVIK_2018_paper_4}
	{0cm}
	{}
\ainput{mftpc/trail-elevator} % Before Jim and Tom's paper
\addpaper
	{The fluint8 software integer library}
	{Jim McCann and Tom Murphy VII}
	{Keywords: uint8\_t, float, binary32, ieee754}
	{SIGBOVIK_2018_paper_18}
	{0cm}
	{}
	\addreview{SIGBOVIK_2018_review_18}{0cm}
\ainput{mftpc/pants-intro} % Before Sol's paper
\addpaper
	{A survey of hardware multithreading}
	{Sol Boucher}
	{Keywords: bend, the, kneedle}
	{SIGBOVIK_2018_paper_EasierChair}
	{0cm}
	{}
	\addreview{SIGBOVIK_2018_review_EasierChair}{0cm}
	\addreview{SIGBOVIK_2018_review_EasierChair-2}{0cm}
\ainput{mftpc/trail-gates}

\addtrack
	{Debugging}{\textit{Amy Likes Spiders}}
\addpaper
	{COBOLd:\ Gobblin' up COBOL bugs for fun and profit}
	{squaresLab and Mr.\ squaresLab SpouseMan}
	{Keywords: software evolution, maintaining software, search-based software engineering, COBOL=\$\$\$\$\$}
	{SIGBOVIK_2018_paper_20}
	{0cm}
	{}
\addpaper
	{Transactional memory concurrency verification with Landslide}
	{Ben Blum}
	{Keywords: landslide terminal, baggage claim, ground transportation, ticketing}
	{SIGBOVIK_2018_paper_13}
	{0cm}
	{}
	\addreview{SIGBOVIK_2018_review_13}{0cm}
\ainput{mftpc/bathroom-stealth}
\ainput{mftpc/pants-single}

\addtrack
	{Programming Languages}{\textit{Save Me}}
\addpaper
	{Dead programming}
	{Michael Coblenz}
	{Keywords: programming languages, live programming, dead programming}
	{SIGBOVIK_2018_paper_25}
	{0cm}
	{}
\addpaper
	{Alternary operators:\ Alternative ternary operators}
	{Jim McCann; Your Name Here; and Your Name Here, Evan}
	{Keywords: ternary, punctuation, operator, punchline}
	{SIGBOVIK_2018_paper_16}
	{0cm}
	{}
\addpaper
	{bashcc:\ Multi-prompt one-shot delimited continuations for Bash}
	{Spencer Baugh and Dougal Pugson}
	{Keywords: control effects, delimited continuations, shell scripting}
	{SIGBOVIK_2018_paper_19}
	{0cm}
	{}
\addpaper
	{Towards a formalization of Claude Shannon's masters thesis}
	{andrewtron3000}
	{Keywords: Coq, proof assistant, formalization, propositional logic, electromechanical relays}
	{SIGBOVIK_2018_paper_7}
	{0cm}
	{}
\ainput{mftpc/slide-dance}
\ainput{mftpc/itg-konami}

\addtrack
	{Metaresearch}{\textit{Literature Club}}
\addpaper
	{Heuristic Ordered-Word Longform Obfuscation, Normally Generated, Creating Abstract
	Nominalizations In Monogrammatic Arrangement Keeping Expected Maximum Yield:\ Study Infers
	Greater Breadth Over Vocabularic Initialization Key Property Regarding Extended
	Sesquipedalian Entries; Notably The Abecedarian Tactics Include Overelaboration, Neologisms,
	Textual Interpretations Twisting Lexical Entries By Eliciting Full Online Resources
	Explaining Possible Exchanges; Often Potential Logorrheic Excesses Require Eventual
	Alternate Listing (Instantiating Zeugma); Energetically Iterating Text Strains Jocularity
	Under Starting Thesis Allocating Humor Until Grand Exit After Conclusion Reaches Obvious
	Nadir Yattering Meaninglessly}
	{Luke Breitfeller}
	{Keywords: SIGBOVIK, study of title, title of study}
	{SIGBOVIK_2018_paper_9}
	{0cm}
	{}
	\addreview{SIGBOVIK_2018_review_9}{0cm}
\ainput{mftpc/trail-helix} % Before Ryan's paper
\addpaper
	{Transparency in research}
	{Ryan Kavanagh}
	{Keywords: transparency, opaqueness, big files}
	{SIGBOVIK_2018_paper_26}
	{0cm}
	{}
\addpaper
	{Academic Advancement Advice:\ Author Articles as A.\ A.}
	{A.\ A.}
	{Keywords: AAA, AAAAA, AAAAAAA}
	{SIGBOVIK_2018_paper_24}
	{0cm}
	{}
	\addreview{SIGBOVIK_2018_review_24}{0cm}
\addpaper
	{A definitely not cherry-picked rhetorical analysis of programming languages reviews}
	{Hannah G.\ Ringler and Stefan Muller}
	{Keywords: reviews, academic memes, reviewer two, cherry-picking}
	{SIGBOVIK_2018_paper_17}
	{0cm}
	{}
	\addreview{SIGBOVIK_2018_review_17}{0cm}
\addpaper
	{Is this the shortest SIGBOVIK paper?}
	{Dicong Qiu}
	{Keywords: shortest, SIGBOVIK, paper}
	{SIGBOVIK_2018_paper_1}
	{0cm}
	{}
	\addreview{SIGBOVIK_2018_review_1}{0cm}
\ainput{mftpc/end-alone}
\ainput{mftpc/end-bathroom}
\ainput{mftpc/end-artisanal}
\ainput{mftpc/end-sigbovik}

>>>>

\renewcommand{\thepage}{\roman{page}}
\setcounter{page}{3}

@@

\addtrack
	{Theory}{\textit{Bottles}}
\addpaper
	{Sublinear colorings of 3-colorable graphs in linear time}
	{Thomas Tseng}
	{Keywords: graph coloring, approximation algorithms, analysis of algorithms}
	{SIGBOVIK_2018_paper_3}
	{0cm}
	{}
\addpaper
	{Cubic partitioning of simultaneous antipodal 4-corner-day time spaces}
	{R.\ Welch and G.\ Ray}
	{Keywords: timecube, conspiracy theories, applied mathematics, applied cubism, tuesdays, meridian time, word animals}
	{SIGBOVIK_2018_paper_2}
	{0cm}
	{}
\addpaper
	{Construction of Eulerian trails in large graphs}
	{Stefan Muller and Ben Blum}
	{Keywords: walk, Eulerian trail, large graph}
	{SIGBOVIK_2018_paper_29}
	{0cm}
	{}
	\addreview{SIGBOVIK_2018_review_29}{0cm}
\addpaper
	{Chess circuits}
	{Ross Dempsey, Sydney Timmerman, and Karl Osterbauer}
	{Keywords: chess, logic, boolean circuits}
	{SIGBOVIK_2018_paper_22}
	{2.5cm}
	{}

\addtrack
	{Cryptocurrencies}{\textit{A Dream}}
\addpaper
	{GradCoin:\ A poor-to-poor electronic cash transfer system}
	{Siddhant Jain}
	{Keywords: blockchain, P2P, digital currency}
	{SIGBOVIK_2018_paper_15}
	{0cm}
	{}
\addpaper
	{CommieCoin:\ Seizing the means of crypto-production}
	{Marx van Raasveldt \textit{et al.}}
	{Keywords: communism, crypto-currency, CommieCoin}
	{SIGBOVIK_2018_paper_11}
	{0cm}
	{}
\addpaper
	{That's Numberwangcoin!}
	{Robert J.\ Simmons}
	{Keywords: boredom, lost coins, shouty bits, speculative investment, the number 2 which you may remember from school is deadly to humans}
	{SIGBOVIK_2018_paper_27}
	{1cm}
	{}

\addtrack
	{Stochastic Processes}{\textit{Portrait of Markov}}
\addpaper
	{Ritwik density estimation and analysis using real techniques}
	{Ritwik Gupta, Ritwik Das, and Ritwik Rajendra}
	{Keywords: Ritwik, Council of Ritwiks, population density, statistical analysis, deep learning, state of the art, monte carlo, bayesian methods, real computational methods and statistics}
	{SIGBOVIK_2018_paper_5}
	{0cm}
	{}
	\addreview{SIGBOVIK_2018_review_5}{0cm}
\addpaper
	{On the intractability of multiclass restroom queues with perfect stall etiquette}
	{Sarah Allen and Ziv Scully}
	{Keywords: Markov chain, recursive renewal-reward, poop}
	{SIGBOVIK_2018_paper_30}
	{0cm}
	{}

\addtrack
	{Ayyy Eye}{\textit{Afterimage of a Crimson Eye}}
\addpaper
	{PSYCHO:\ PerSonalitY CHaracterizatiOn of artificial intelligence}
	{Achal Dave and Rohit Girdhar}
	{Keywords: interpretability, psychology, deep learning, artificial intelligence, rorschach}
	{SIGBOVIK_2018_paper_8}
	{0cm}
	{}
\addpaper
	{The NUGGET non-linear piecewise activation}
	{Stephen Merity}
	{Keywords: deep learning, neural networks, nugget, nuggets, chicken nuggets, smart}
	{SIGBOVIK_2018_paper_10}
	{0cm}
	{}
\addpaper
	{Substitute teacher networks:\ Learning with almost no supervision}
	{Samuel Albanie, James Thewlis, and Jo\~ao F.\ Henriques}
	{Keywords: substitute, teacher, networks}
	{SIGBOVIK_2018_paper_28}
	{1cm}
	{}
	\addreview{SIGBOVIK_2018_review_28}{0cm}

\addtrack
	{Parapsychology}{\textit{Get Out of My Head}}
\addpaper
	{This grad student studied parapsychology---and you won't believe what he found}
	{David Edelstein}
	{Keywords: parapsychology, science, experimental design, experimenter effects, philosophy, telepathy}
	{SIGBOVIK_2018_paper_23}
	{0cm}
	{}
	\addreview{SIGBOVIK_2018_review_23}{0cm}

\addtrack
	{Art}{\textit{Open Your Third Eye}}
\addpaper
	{Automating art snobbiness:\ Dead duck or phoenix?}
	{Dion Ysus and Oscar I.\ Hernandez}
	{Keywords: automation, art, elite, 1337 dankster, cicada 3301, de Bruijn sequence}
	{SIGBOVIK_2018_paper_14}
	{0cm}
	{}
	\addreview{SIGBOVIK_2018_review_14}{0cm}
\addpaper
	{Toward a historically faithful performance of the piano works of Anton\'in Qwe\v{r}t\'y}
	{William Gunther and Brian Kell}
	{Keywords: G-flat major, F-sharp minor, A-flat harmonic major $\flat$6 $\flat$5, G-sharp harmonic major $\flat$5}
	{SIGBOVIK_2018_paper_21}
	{0cm}
	{}
	\addreview{SIGBOVIK_2018_review_21}{0cm}
\addpaper
	{WordTeX:\ A WYSIPCTWOTCG typesetting tool}
	{Tom Wildenhain}
	{Keywords: Word, Microsoft Word, LaTeX, WordTeX}
	{SIGBOVIK_2018_paper_12}
	{0cm}
	{}
	\addreview{SIGBOVIK_2018_review_12}{0cm}

@@

\addtrack
	{Systems}{\textit{Wheel}}
\addpaper
	{mallocd:\ designing a garbage-free nosql data store}
	{igor}
	{Keywords: state-of-the-art, in-memory, garbage-free, cloud-native, nosql, bare metal, containerless, micro-service, data store}
	{SIGBOVIK_2018_paper_4}
	{0cm}
	{}
\addpaper
	{The fluint8 software integer library}
	{Jim McCann and Tom Murphy VII}
	{Keywords: uint8\_t, float, binary32, ieee754}
	{SIGBOVIK_2018_paper_18}
	{0cm}
	{}
	\addreview{SIGBOVIK_2018_review_18}{0cm}
\addpaper
	{A survey of hardware multithreading}
	{Sol Boucher}
	{Keywords: bend, the, kneedle}
	{SIGBOVIK_2018_paper_EasierChair}
	{0cm}
	{}
	\addreview{SIGBOVIK_2018_review_EasierChair}{0cm}
	\addreview{SIGBOVIK_2018_review_EasierChair-2}{0cm}

\addtrack
	{Debugging}{\textit{Amy Likes Spiders}}
\addpaper
	{COBOLd:\ Gobblin' up COBOL bugs for fun and profit}
	{squaresLab and Mr.\ squaresLab SpouseMan}
	{Keywords: software evolution, maintaining software, search-based software engineering, COBOL=\$\$\$\$\$}
	{SIGBOVIK_2018_paper_20}
	{0cm}
	{}
\addpaper
	{Transactional memory concurrency verification with Landslide}
	{Ben Blum}
	{Keywords: landslide terminal, baggage claim, ground transportation, ticketing}
	{SIGBOVIK_2018_paper_13}
	{0cm}
	{}
	\addreview{SIGBOVIK_2018_review_13}{0cm}

\addtrack
	{Programming Languages}{\textit{Save Me}}
\addpaper
	{Dead programming}
	{Michael Coblenz}
	{Keywords: programming languages, live programming, dead programming}
	{SIGBOVIK_2018_paper_25}
	{0cm}
	{}
\addpaper
	{Alternary operators:\ Alternative ternary operators}
	{Jim McCann; Your Name Here; and Your Name Here, Evan}
	{Keywords: ternary, punctuation, operator, punchline}
	{SIGBOVIK_2018_paper_16}
	{0cm}
	{}
\addpaper
	{bashcc:\ Multi-prompt one-shot delimited continuations for Bash}
	{Spencer Baugh and Dougal Pugson}
	{Keywords: control effects, delimited continuations, shell scripting}
	{SIGBOVIK_2018_paper_19}
	{0cm}
	{}
\addpaper
	{Towards a formalization of Claude Shannon's masters thesis}
	{andrewtron3000}
	{Keywords: Coq, proof assistant, formalization, propositional logic, electromechanical relays}
	{SIGBOVIK_2018_paper_7}
	{0cm}
	{}

\addtrack
	{Metaresearch}{\textit{Literature Club}}
\addpaper
	{Heuristic Ordered-Word Longform Obfuscation, Normally Generated, Creating Abstract
	Nominalizations In Monogrammatic Arrangement Keeping Expected Maximum Yield:\ Study Infers
	Greater Breadth Over Vocabularic Initialization Key Property Regarding Extended
	Sesquipedalian Entries; Notably The Abecedarian Tactics Include Overelaboration, Neologisms,
	Textual Interpretations Twisting Lexical Entries By Eliciting Full Online Resources
	Explaining Possible Exchanges; Often Potential Logorrheic Excesses Require Eventual
	Alternate Listing (Instantiating Zeugma); Energetically Iterating Text Strains Jocularity
	Under Starting Thesis Allocating Humor Until Grand Exit After Conclusion Reaches Obvious
	Nadir Yattering Meaninglessly}
	{Luke Breitfeller}
	{Keywords: SIGBOVIK, study of title, title of study}
	{SIGBOVIK_2018_paper_9}
	{0cm}
	{}
	\addreview{SIGBOVIK_2018_review_9}{0cm}
\addpaper
	{Transparency in research}
	{Ryan Kavanagh}
	{Keywords: transparency, opaqueness, big files}
	{SIGBOVIK_2018_paper_26}
	{0cm}
	{}
\addpaper
	{Academic Advancement Advice:\ Author Articles as A.\ A.}
	{A.\ A.}
	{Keywords: AAA, AAAAA, AAAAAAA}
	{SIGBOVIK_2018_paper_24}
	{0cm}
	{}
	\addreview{SIGBOVIK_2018_review_24}{0cm}
\addpaper
	{A definitely not cherry-picked rhetorical analysis of programming languages reviews}
	{Hannah G.\ Ringler and Stefan Muller}
	{Keywords: reviews, academic memes, reviewer two, cherry-picking}
	{SIGBOVIK_2018_paper_17}
	{0cm}
	{}
	\addreview{SIGBOVIK_2018_review_17}{0cm}
\addpaper
	{Is this the shortest SIGBOVIK paper?}
	{Dicong Qiu}
	{Keywords: shortest, SIGBOVIK, paper}
	{SIGBOVIK_2018_paper_1}
	{0cm}
	{}
	\addreview{SIGBOVIK_2018_review_1}{0cm}
